Exploratory data analysis

### 2021-07-21 slides/data_checking.Rmd
add lmer for resp_conf ~ acc_recall * j_score
add couple demos graphs

demos_ids <- read_csv(here::here("ignore", "data", "demos_ids.csv"))
q_google_demos <- read_csv(here::here("ignore", "data", "q_google_demos.csv")) %>% 
  right_join(demos_ids, by = "demographics_id")

@@

@@

```{r}
q_trivia_demos %>% 
  ggplot(aes(x = trivia_skill_self, y = j_score)) +
  geom_abline(slope = .01, intercept = 0, linetype = "dotted") +
  geom_point(size = 3) +
  expand_limits(y = 0) +
  labs(x = "Self-reported trivia expertise (relative to 'average person')",
       y = "Expertise score on Jeopardy audition test") +
  theme_bw()
```

@@

```{r}
j_recall %>% 
  left_join(q_google_demos %>% mutate(subj_num = factor(subj_num)), by = "subj_num") %>% 
  ggplot(aes(x = resp_conf, y = as.integer(acc_recall), color = gender, fill = gender)) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), se = FALSE) +
  labs(x = "Recall confidence", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
  theme_bw()
```

>>>>

demos_ids <- read_csv(here::here("ignore", "data", "demos_ids.csv"))
q_google_demos <- read_csv(here::here("ignore", "data", "q_google_demos.csv")) %>% 
  right_join(demos_ids, by = "demographics_id") %>% 
  mutate(subj_num = factor(subj_num))

@@

# Demographics

### What is the age and gender breakdown?

```{r}
q_google_demos %>% 
  ggplot(aes(x = age, fill = gender)) +
  geom_histogram(position = "identity", alpha = 0.5)
```

@@

```{r}
q_trivia_demos %>% 
  left_join(q_google_demos, by = "subj_num") %>% 
  ggplot(aes(x = trivia_skill_self, y = j_score)) +
  # geom_abline(slope = .01, intercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 75, linetype = "dotted") +
  geom_hline(yintercept = 0.7, linetype = "dotted") +
  geom_point(aes(color = gender), size = 2, alpha = 0.7) +
  geom_smooth(method = "lm", formula = y ~ x) +
  expand_limits(y = 0) +
  labs(x = "Self-reported trivia expertise (relative to 'average person')",
       y = "Expertise score on Jeopardy audition test") +
  theme_bw()
```

@@

```{r}
j_recall %>% 
  mutate(acc_recall = as.integer(acc_recall),
         j_score = j_score - 0.5) %>% 
  lme4::lmer(resp_conf ~ acc_recall * j_score + (1 + acc_recall | subj_num), data = .) %>% 
  summary()
```

```{r}
j_recall %>% 
  left_join(q_google_demos, by = "subj_num") %>% 
  ggplot(aes(x = resp_conf, y = as.integer(acc_recall), color = gender, fill = gender)) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), se = FALSE) +
  labs(x = "Recall confidence", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
  theme_bw()
```

```{r}
j_recall %>% 
  left_join(q_google_demos, by = "subj_num") %>% 
  ggplot(aes(x = acc_recall, y = resp_conf, color = gender)) + 
  geom_jitter(alpha = 0.3, width = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "lm", formula = y ~ x, se = FALSE, size = 0.5) + 
  labs(x = "Recall accuracy (strict)", y = "Recall confidence", color = "Expertise score", fill = "Expertise score") +
  theme_bw()
```
